Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2025-03-14 paper/1_Initial/manuscript.qmd
minor

By combining network analysis with psychometric methods, the recently-developed EGA framework that allows to jointly estimate the number of dimensions (i.e., groups of items), the structure as well as its stability [@golino2017exploratory; @golino2020investigating]. Evidence has underlined its suitability as an alternative to traditional factor analysis, addressing some of its limitations such as the assumption of a "latent" source of variability, possible biasing in the estimation of the optimal factor numbers depending on sample size, and **TODO: a third example would be nice?** **REF**, while remaining comparable and interpretable [@christensen2021equivalency]. At a fundamental level, EGA conceptualizes variables as nodes in a network, with connections (edges) reflecting associations between them. Clustering these nodes reveals distinct communities of related items, in practice akin to traditional latent factors - but without explicitly assuming their presence [@christensen2021equivalency].

>>>>

By combining network analysis with psychometric methods, the recently-developed EGA framework allows to jointly estimate the number of dimensions (i.e., groups of items), the structure as well as its stability [@golino2017exploratory; @golino2020investigating]. Evidence has underlined its suitability as an alternative to traditional factor analysis, addressing some of its limitations such as the assumption of a "latent" source of variability, possible biasing in the estimation of the optimal factor numbers depending on sample size, and **TODO: a third example would be nice?** **REF**, while remaining comparable and interpretable [@christensen2021equivalency]. At a fundamental level, EGA conceptualizes variables as nodes in a network, with connections (edges) reflecting associations between them. Clustering these nodes reveals distinct communities of related items, in practice akin to traditional latent factors - but without explicitly assuming their presence [@christensen2021equivalency].
